Graph Exploration and Search

### 2017-11-08 exploratory.tex
Small change

\stitle{Example-based approaches.} 
One of the earliest attempts to bring examples as a query method is query-by-example~\citep{zloof1975query}.
The main idea was to help the user in the query formulation, allowing her to specify the shape of the results in terms of templates for tuples, i.e., examples.
Query-by-example has been lately revisited, and the use of examples have found application in graph data as well. 
The definition of example has transformed from a mere template to the representative of the intended results the user would like to have.
\emph{Examples} for a graph $G = (V,E)$ can be either \emph{set of nodes} $Q \subseteq V$, or \emph{subgraphs} $Q \subseteq G$, where with an abuse of notation $\subseteq$ indicates both set and structural inclusion.

>>>>

\stitle{Example-based approaches.} 
One of the earliest attempts to bring examples as a query method is query-by-example~\citep{zloof1975query}.
The main idea was to help the user in the query formulation, allowing her to specify the shape of the results in terms of templates for tuples, i.e., examples.
Query-by-example has been lately revisited, and the use of examples have found application in graph data as well. 
The definition of example has transformed from a mere template to the representative of the intended results the user would like to have.
\emph{Examples} for a graph $G = (V,E)$ can be either \emph{set of nodes} $Q \subseteq V$, \emph{tuple} of nodes $(v_1, ..., v_n) \in V^n$ or \emph{subgraphs} $Q \subseteq G$, where with an abuse of notation $\subseteq$ indicates both set and structural inclusion.
